Dependently Typed Languages in Statix

### 2023-04-22 pres-thesis/presentation.tex
Finish presentation draft

\title[]{Dependently Typed Languages in Statix}
\institute[]{Delft University of Technology, The Netherlands}
\author{Jonathan Brouwer \and Jesper Cockx \and Aron Zwaan}

@@

\begin{frame}[fragile]{Type Checking: Variable Capturing}
	todo
\end{frame}

@@

@@

\begin{frame}{Comparison with LambdaPi}
	\begin{itemize}
		\item A \emph{logical framework} in which you can embed other programming languages
		\item Supports rewrite rules
		\item Cannot define \emph{Let} because of limitations of LambdaP
	\end{itemize}
\end{frame}

\begin{frame}{Comparison with LambdaPi: Example}

\begin{frame}{Inductive Data Types}
	todo
\end{frame}

\begin{frame}{Interpreter \& Compiler}
	todo
\end{frame}

>>>>

\title[]{Dependently Typed Languages in Statix}
\institute[]{Delft University of Technology, The Netherlands}
\author{Jonathan Brouwer}

@@

\begin{frame}[fragile]{Type Checking: Variable Capturing}
	\begin{exampleblock}{What is the type of this expression?}
		\texttt{$\backslash$T : Type. $\backslash$T : T. T}
	\end{exampleblock}
\end{frame}

\begin{frame}[fragile]{Type Checking: Variable Capturing}
	\begin{exampleblock}{What is the type of this expression?}
		\texttt{$\backslash$T : Type. $\backslash$T : T. T}
	\end{exampleblock}

	\begin{block}{The type}
		\texttt{T : Type -> T : T -> T}
	\end{block}

	\begin{block}{Equivalent type under renaming: Not correct!}
		\texttt{T : Type -> x : T -> x}
	\end{block}
\end{frame}

\begin{frame}[fragile]{Type Checking: Variable Capturing}
	\begin{block}{Solutions}
		\begin{enumerate}
			\item De Bruijn indices
			\item Uniquifying names
			\item Capture-avoiding substitution
			\item \textbf{Using scopes to distinguish names}
		\end{enumerate}
	\end{block}
\end{frame}

@@

\begin{frame}{On Extensibility}
	\begin{block}{How to extend the language}
		\begin{enumerate}
			\item Define the parsing rules for the new feature
			\item Create a new .stx file for the type-checking rules (and import it)
			\item Define the relations (typeOfExpr, betaReduceHead, expectBetaEq and betaReduce) in this file using the defining inference rules
		\end{enumerate}
	\end{block}
\end{frame}

@@

\begin{frame}{Comparison with LambdaPi}
	\begin{itemize}
		\item A \emph{logical framework} in which you can embed other programming languages
		\item Supports rewrite rules
		\item Cannot define \emph{Let} because of limitations of LambdaPi
	\end{itemize}
\end{frame}

\begin{frame}{Comparison with LambdaPi: Example}
	\begin{exampleblock}{Defining FnConstruct}
		\texttt{symbol FnConstruct :
		\\\hspace{1em}Π (A : TmSort ),
		\\\hspace{1em}Π (B : TmType A → TmSort ),
		\\\hspace{1em}Π (f : Π (x : TmType A), TmType (B x)),
		\\\hspace{1em}TmType ( FnType A B);
		}

	\end{exampleblock}

	\begin{exampleblock}{Reduction rule for FnConstruct}
		\texttt{rule FnConstruct \_ \_ \$f → \$f;}
	\end{exampleblock}
\end{frame}
